Early environmental conditions do not impact behavioural flexibility in an invasive and non-invasive lizard species

### 2024-11-09 ms.qmd
Updates

```{r, sampleSize}
#| label: sampleSize
# List with the sample sizes from the database (here("output/databases_clean/data_asso.csv") as the sample size per species and group is the same on each task. We used function sample (see func.R) to estimate the sample size per treatment and species.
source(here("R", "func.R"))
#
specie <- c("delicata", "guichenoti")
hormone <- c("CORT", "Control")
temperature <- c("Cold", "Hot")
#
n_list <- list()
#
for(i in 1:length(specie)){
  for(k in 1:length(hormone)){
    for(l in 1:length(temperature)){
      n_list[[paste(specie[i], hormone[k], temperature[l], sep = "_")]] <- sample(clean_df, specie[i], hormone[k], temperature[l])
      }
    }
  }
```

@@

We started with 96 lizards, 48 per species and 12 per treatment per species. However, our final sample size was 81 due to natural mortality (n = 11), failure to complete the training stage (n = 1), or because the number of failed tasks (see above) was higher than 15 (n = 3). The final sample sizes per treatment and species are listed in @fig-results. These animals came from a total of `r deli_clutches` clutches in _L. delicata_ and `r guich_clutches` in _L. guichenoti_.

@@

```{r, fig_rawdata}
#| label: fig_rawdata
#| fig.cap: "Probability of choosing correctly over trials for each of the treatments and species. The dots represent the proportion of individuals per trial that chose correctly while the lines show the mean predicted probability of choosing correctly, estimated using the posteriors of our model."
#
# Load the data
data_raw <- clean_df %>%
  group_by(species, trt, trial_reversal) %>%
  summarize(prop_correct = mean(FC_reversal, na.rm = TRUE)) %>%
  mutate(trt = factor(trt, 
          levels = c("A_23", "B_23", "A_28", "B_28"), 
          labels = c("CORT-Cold", "Control-Cold", "CORT-Hot", "Control-Hot")),
        species = factor(species,
          levels = c("delicata", "guichenoti"),
          labels = c("italic('L. delicata')", "italic('L. guichenoti')"))) %>%
  rename(Trial = trial_reversal,
         Treatment = trt) %>%
data.frame()
#
# Get the df for the predicted prob
df_deliprob$species <- "italic('L. delicata')"
df_guichprob$species <- "italic('L. guichenoti')"
df_combined <- rbind(df_deliprob, df_guichprob)
df_all <- full_join(df_combined, data_raw, by = c("Trial", "Treatment", "species"))
# Plot the raw data for the reversal tasks for both species with the predicted prob
plot_raw <- ggplot(data = df_all, aes(x = Trial, y = Mean_Predicted_prob, color = Treatment, fill = Treatment)) +
  geom_smooth(linewidth = 1) +
  geom_point(data = df_all, aes(x = Trial, y = prop_correct, color = Treatment, fill = Treatment)) +
  scale_color_manual(values = c("darkblue", "#68bde1", "#b50101", "#fa927d")) +
  scale_fill_manual(values = c("darkblue", "#68bde1", "#b50101", "#fa927d")) +
  facet_grid(species ~ Treatment, labeller = label_parsed, switch = "y") +
  labs(x = "Trial", y = "Proportion of correct choices", color = "Treatments", fill = "Treatments") +
  theme_classic()
#
# Save the plot
ggsave("./output/figures/plot_raw.png", plot=plot_raw, width = 25, height = 18, units = "cm", dpi = 600)
knitr::include_graphics("./output/figures/plot_raw.png")
```

>>>>

```{r, sampleSize}
#| label: sampleSize
# List with the sample sizes from the database (here("output/databases_clean/data_asso.csv") as the sample size per species and group is the same on each task. We used function sample (see func.R) to estimate the sample size per treatment and species.
source(here("R", "func.R"))
#
specie <- c("delicata", "guichenoti")
hormone <- c("CORT", "Control")
temperature <- c("Cold", "Hot")
#
n_list <- list()
#
for(i in 1:length(specie)){
  for(k in 1:length(hormone)){
    for(l in 1:length(temperature)){
      n_list[[paste(specie[i], hormone[k], temperature[l], sep = "_")]] <- sample(clean_df, specie[i], hormone[k], temperature[l])
      }
    }
  }

a <- n_list$delicata_CORT_Cold + n_list$delicata_CORT_Hot + n_list$delicata_Control_Cold + n_list$delicata_Control_Hot + n_list$guichenoti_CORT_Cold + n_list$guichenoti_CORT_Hot + n_list$guichenoti_Control_Cold + n_list$guichenoti_Control_Hot

n_list_2 <- list()
#
b <- unique(data$lizard_id)
```

@@

We started with 96 lizards, 48 per species and 12 per treatment per species. However, our final sample size was 84 due to natural mortality (n = 11), failure to complete the training stage (n = 1), or because the number of failed tasks (see above) was higher than 15 (n = 0). The final sample sizes per treatment and species are listed in @fig-results. These animals came from a total of `r deli_clutches` clutches in _L. delicata_ and `r guich_clutches` in _L. guichenoti_.

@@

```{r, fig-rawdata}
#| label: fig-rawdata
#| fig.cap: "Probability of choosing correctly over trials for each of the treatments and species. The dots represent the proportion of individuals per trial that chose correctly while the lines show the mean predicted probability of choosing correctly, estimated using the posteriors of our model."
#
# Load the data
data_raw <- clean_df %>%
  group_by(species, trt, trial_reversal) %>%
  summarize(prop_correct = mean(FC_reversal, na.rm = TRUE)) %>%
  mutate(trt = factor(trt, 
          levels = c("A_23", "B_23", "A_28", "B_28"), 
          labels = c("CORT-Cold", "Control-Cold", "CORT-Hot", "Control-Hot")),
        species = factor(species,
          levels = c("delicata", "guichenoti"),
          labels = c("italic('L. delicata')", "italic('L. guichenoti')"))) %>%
  rename(Trial = trial_reversal,
         Treatment = trt) %>%
data.frame()
#
# Get the df for the predicted prob
df_deliprob$species <- "italic('L. delicata')"
df_guichprob$species <- "italic('L. guichenoti')"
df_combined <- rbind(df_deliprob, df_guichprob)
df_all <- full_join(df_combined, data_raw, by = c("Trial", "Treatment", "species"))
# Plot the raw data for the reversal tasks for both species with the predicted prob
plot_raw <- ggplot(data = df_all, aes(x = Trial, y = Mean_Predicted_prob, color = Treatment, fill = Treatment)) +
  geom_smooth(linewidth = 1) +
  geom_point(data = df_all, aes(x = Trial, y = prop_correct, color = Treatment, fill = Treatment)) +
  scale_color_manual(values = c("darkblue", "#68bde1", "#b50101", "#fa927d")) +
  scale_fill_manual(values = c("darkblue", "#68bde1", "#b50101", "#fa927d")) +
  facet_grid(species ~ Treatment, labeller = label_parsed, switch = "y") +
  labs(x = "Trial", y = "Proportion of correct choices", color = "Treatments", fill = "Treatments") +
  theme_classic()
#
# Save the plot
ggsave("./output/figures/plot_raw.png", plot=plot_raw, width = 25, height = 18, units = "cm", dpi = 600)
knitr::include_graphics("./output/figures/plot_raw.png")
```
